# GET ALBUM DATA FROM SPOTIFY

```{r message=FALSE}
################################################################################################################
# Load libraries
################################################################################################################
library(spotifyr)
library(tidyverse)
```

```{r}
# Get a vector of all the artists that have been nominated for AOTY. We will loop through them below.
aoty_clean <- readRDS("AOTY/aoty_clean.RDS")

artists <- unique(aoty_clean$Artist)
```

```{r}
# The loop below crashes for the following artists, so I need to remove them for now and manually pull them later.
artists_new <- artists[-c(6, 11, 69, 83, 92, 108, 127, 129, 135, 138, 152, 153, 162, 185, 193, 212, 216)]
```

## Run Initial Spotify Loop
```{r}
################################################################################################################
# Grab all albums for all of the artists specified above.
# The function `get_artist_audio_features` was used because it allows us to specify the artist's name
# rather than having to look up and input their Spotify ID.
################################################################################################################
albums <- data.frame()
for (i in 1:length(artists_new)) {
    out <- get_artist_audio_features(artist = artists_new[i])
    albums <- rbind(albums, out)
}
```

```{r}
# Select only the variables of interest
albums_clean <- cbind(Artist = albums$artist_name,
                 ID = albums$artist_id,
                 Album = albums$album_name,
                 Song = albums$track_name,
                 Danceability = albums$danceability,
                 Energy = albums$energy,
                 Loudness = albums$loudness,
                 Speechiness = albums$speechiness,
                 Acousticness = albums$acousticness,
                 Instrumentalness = albums$instrumentalness,
                 Liveness = albums$liveness,
                 Valence = albums$valence,
                 Tempo = albums$tempo,
                 Duration = albums$duration_ms,
                 Explicit = albums$explicit)
```

```{r}
# Convert to a data frame
albums_clean <- as.data.frame(albums_clean)
```

## Manually Grab the Rest of the Artists
These are the names of the artists that weren't found in in the initial loop:
```{r}
artists[c(6, 11, 69, 83, 92, 108, 127, 129, 135, 138, 152, 153, 162, 185, 193, 212, 216)]
```
A few notes:

Ray Charles & Various Artists -- already found relevant album info under Ray Charles
Quincy Jones & Various Artists  -- already found relevant album info under Quincy Jones
USA For Africa -- Couldn't find the full album on Spotify.
The Singing Nun -- Couldn't find the full album on Spotify.
The Swingle Singers	-- Couldn't find the full album on Spotify.
Various Artists: Jesus Christ Superstar (London Production) 1972 -- Couldn't find this specific album
Various Artists: Jesus Christ Superstar (Original Broadway Cast Recording)	1973 -- Couldn't find this specific album
Ray Charles: genius+soul=jazz	-- Couldn't find the full album on Spotify.

All others are coded below.
In most cases, I had to look up the relevant album ID on Spotify and pull it directly.
For a few cases, I was able to use the `get_artist_audio_features` using a simplified name
(i.e. "Black Eyed Peas" instead of "The Black Eyed Peas")
```{r}
# 7 - Lil Nas X

# This pulls every track on the album
lil_nas_x <- spotifyr::get_album_tracks("4IRiXE5NROxknUSAUSjMoO") 
lil_nas_x$Artist <- "Lil Nas X"
lil_nas_x$Album <- "7"

# This (separately) pulls all of the audio features for each song on the album
audio <- spotifyr::get_track_audio_features(lil_nas_x$id) 

# Join the data together
lil_nas_x <- left_join(lil_nas_x, audio, by = "id")

# Grab only the relevant variables
lil_nas_x_clean <- lil_nas_x %>% 
  select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# The Black Eyed Peas
bep <- get_artist_audio_features("Black Eyed Peas")
```

```{r}
# Raising Sand - Robert Plant & Alison Krauss
robert_plant <- spotifyr::get_album_tracks("54GfJ3ZEY2b6PKmvETmj1n")
robert_plant$Artist <- "Robert Plant & Alison Krauss"
robert_plant$Album <- "Raising Sand"

audio <- spotifyr::get_track_audio_features(robert_plant$id)

robert_plant <- left_join(robert_plant, audio, by = "id")

robert_plant_clean <- robert_plant %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# The 3 Tenors in Concert 1994 - José Carreras, Plácido Domingo & Luciano Pavarotti with Zubin Mehta
three_tenors <- spotifyr::get_album_tracks("4M1xaHN4ztbVWmyxPVNibu")
three_tenors$Artist <- "José Carreras, Plácido Domingo & Luciano Pavarotti with Zubin Mehta"
three_tenors$Album <- "The 3 Tenors in Concert 1994"

audio <- spotifyr::get_track_audio_features(three_tenors$id)

three_tenors <- left_join(three_tenors, audio, by = "id")

three_tenors_clean <- three_tenors %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# The Concert for Bangladesh - George Harrison & Friends
george_harrison <- spotifyr::get_album_tracks("3tcy7Al4hBYMaIYraZhexu")
george_harrison$Artist <- "George Harrison & Friends (Ravi Shankar, Bob Dylan, Leon Russell, Ringo Starr, Billy Preston, Eric Clapton & Klaus Voormann)"
george_harrison$Album <- "The Concert for Bangladesh"

audio <- spotifyr::get_track_audio_features(george_harrison$id)

george_harrison <- left_join(george_harrison, audio, by = "id")

george_harrison_clean <- george_harrison %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# The First Family - Vaughn Meader
vaughn_meader <- get_album_tracks("5QN8u21tWltIeNTqVTmDKV")
vaughn_meader$Artist <- "Vaughn Meader"
vaughn_meader$Album <- "The First Family"

audio <- spotifyr::get_track_audio_features(vaughn_meader$id)

vaughn_meader <- left_join(vaughn_meader, audio, by = "id")

vaughn_meader_clean <- vaughn_meader %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Getz/Gilberto - Stan Getz & João Gilberto
stan_getz <- get_artist_audio_features("Stan Getz")
```

```{r}
# Trio - Dolly Parton, Linda Ronstadt, & Emmylou Harris
trio <- spotifyr::get_album_tracks("1uPjtjcaOwsxwLO7DzwQh2")
trio$Artist <- "Dolly Parton, Linda Ronstadt, & Emmylou Harris"
trio$Album <- "Trio"

audio <- spotifyr::get_track_audio_features(trio$id)

trio <- left_join(trio, audio, by = "id")

trio_clean <- trio %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Paul McCartney
paul_mccartney <- get_artist_audio_features("Paul McCartney")
```

```{r}
# John Williams
john_williams <- get_artist_audio_features("John Williams")
```

```{r}
# Great Band with Great Voices - Si Zentner & the Johnny Mann Singers
si_zentner <- spotifyr::get_album_tracks("52a7wxVQoJuGkoxkp7RMbD")
si_zentner$Artist <- "Si Zentner & the Johnny Mann Singers"
si_zentner$Album <- "Great Band with Great Voices"

audio <- spotifyr::get_track_audio_features(si_zentner$id)

si_zentner <- left_join(si_zentner, audio, by = "id")

si_zentner_clean <- si_zentner %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Francis Albert Sinatra & Antonio Carlos Jobim - Frank Sinatra & Antonio Carlos Jobim
frank_sinatra <- spotifyr::get_album_tracks("0LYpJGx3fHoTmKOtKuMWtQ")
frank_sinatra$Artist <- "Frank Sinatra & Antonio Carlos Jobim"
frank_sinatra$Album <- "Francis Albert Sinatra & Antonio Carlos Jobim"

audio <- spotifyr::get_track_audio_features(frank_sinatra$id)

frank_sinatra <- left_join(frank_sinatra, audio, by = "id")

frank_sinatra_clean <- frank_sinatra %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Bind all of the data together for cases where I just used `get_artist_audio_features`
raw_df <- rbind(bep, stan_getz, paul_mccartney, john_williams)

clean_df_1 <- cbind(Artist = raw_df$artist_name,
                 Album = raw_df$album_name,
                 Song = raw_df$track_name,
                 Danceability = raw_df$danceability,
                 Energy = raw_df$energy,
                 Loudness = raw_df$loudness,
                 Speechiness = raw_df$speechiness,
                 Acousticness = raw_df$acousticness,
                 Instrumentalness = raw_df$instrumentalness,
                 Liveness = raw_df$liveness,
                 Valence = raw_df$valence,
                 Tempo = raw_df$tempo,
                 Duration = raw_df$duration_ms,
                 Explicit = raw_df$explicit)

clean_df_1 <- as.data.frame(clean_df_1)
```

```{r}
# Bind all of the data together for cases where I had to pull a specific album title
raw_df_2 <- rbind(lil_nas_x_clean, robert_plant_clean, three_tenors_clean, 
                  george_harrison_clean, vaughn_meader_clean,
                  trio_clean, si_zentner_clean, frank_sinatra_clean)

clean_df_2 <- cbind(Artist = raw_df_2$Artist,
                 Album = raw_df_2$Album,
                 Song = raw_df_2$name,
                 Danceability = raw_df_2$danceability,
                 Energy = raw_df_2$energy,
                 Loudness = raw_df_2$loudness,
                 Speechiness = raw_df_2$speechiness,
                 Acousticness = raw_df_2$acousticness,
                 Instrumentalness = raw_df_2$instrumentalness,
                 Liveness = raw_df_2$liveness,
                 Valence = raw_df_2$valence,
                 Tempo = raw_df_2$tempo,
                 Duration = raw_df_2$duration_ms.x,
                 Explicit = raw_df_2$explicit)

clean_df_2 <- as.data.frame(clean_df_2)
```

```{r}
# Join everything together
albums <- rbind(albums, clean_df_1, clean_df_2)

# The loop grabbed a number of duplicates, so I will remove them here
albums <- distinct(albums)
```
-----------
```{r}
#I keep getting an error when doing the initial for loop to get albums so I'm uploading your albums csv and adding on missing albums to the csv
setwd("/Users/bolee/Desktop/QMSS/Spring20/DataViz/Group_R_Spotify")
albums <- read.csv("Spotify_Albums/albums.csv")
```

Adding artists from the AOTY dataframe that are missing in the initial pull of the albums dataframe

```{r}
# Al Hirt
al_hirt <- get_artist_audio_features("Al Hirt")
```

```{r}
# Alanis Morissette
alanis_morissette <- get_artist_audio_features("Alanis Morissette")
```

```{r}
# Alicia Keys
alicia_keys <- get_artist_audio_features("Alicia Keys")
```

```{r}
# Allan Sherman
allan_sherman <- get_artist_audio_features("Allan Sherman")
```

```{r}
# Amy Grant
amy_grant <- get_artist_audio_features("Amy Grant")
```

```{r}
# Amy Winehouse
amy_winehouse <- get_artist_audio_features("Amy Winehouse")
```

```{r}
# Andy Williams
andy_williams <- get_artist_audio_features("Andy Williams")
```

```{r}
# Babyface
babyface <- get_artist_audio_features("Babyface")
```

```{r}
# Barry Manilow
barry_manilow <- get_artist_audio_features("Barry Manilow")
```

```{r}
# Bette Midler
bette_middler <- get_artist_audio_features("Bette Middler")
```

```{r}
# Billy Joel
billy_joel <- get_artist_audio_features("Billy Joel")
```

```{r}
# Blood, Sweat & Tears
blood_sweat_tears <- get_artist_audio_features("Blood, Sweat & Tears")
```

```{r}
# Bob Newhart
bob_newhart <- get_artist_audio_features("Bob Newhart")
```

```{r}
# Bobbie Gentry
bobbie_gentry <- get_artist_audio_features("bobbie_gentry")
```

```{r}
# Bobby McFerrin
bobby_mcferrin <- get_artist_audio_features("Bobby McFerrin")
```

```{r}
# Bonnie Raitt
bonnie_raitt <- get_artist_audio_features("Bonnie Raitt")
```

```{r}
# Boz Scaggs
boz_scaggs <- get_artist_audio_features("Boz Scaggs")
```

```{r}
# Carpenters
carpenters <- get_artist_audio_features("Carpenters")
```

```{r}
# Celine Dion
celine_dion <- get_artist_audio_features("Celine Dion")
```

```{r}
# Charlie Rich
charlie_rich <- get_artist_audio_features("Charlie Rich")
```

```{r}
# Chicago
chicago <- get_artist_audio_features("chicago")
```

```{r}
# Christopher Cross
christopher_cross <- get_artist_audio_features("Christopher Cross")
```

```{r}
# Coldplay
coldplay <- get_artist_audio_features("Coldplay")
```

```{r}
# Crosby, Stills & Nash
crosby_stills_nash <- get_artist_audio_features("Crosby, Stills & Nash")
```

```{r}
# Crosby, Stills, Nash, & Young
crosby_stills_nash_young <- get_artist_audio_features("Crosby, Stills, Nash, & Young")
```

```{r}
# Dire Straits
dire_straits <- get_artist_audio_features("Dire Straits")
```

```{r}
# Don Henley
don_henley <- get_artist_audio_features("Don Henley")
```

```{r}
# Don McLean
don_mclean <- get_artist_audio_features("Don McLean")
```

```{r}
# Donald Fagen
donald_fagen <- get_artist_audio_features("Donald Fagen")
```

```{r}
# Eagles
eagles <- get_artist_audio_features("Eagles")
```

```{r}
# Ed Ames
ed_ames <- get_artist_audio_features("Ed_Ames")
```

```{r}
# Eddy Arnold
eddy_arnold <- get_artist_audio_features("Eddy Arnold")
```

```{r}
# Elton John
elton_john <- get_artist_audio_features("Elton John")
``` 	

```{r}
# Eric Clapton
eric_clapton <- get_artist_audio_features("Eric Clapton")
```

```{r}
# Erich Leinsdorf
erich_leinsdorf <- get_artist_audio_features("Erich Leinsdorf")
```

```{r}
# Fine Young Cannibals
fine_young_cannibals <- get_artist_audio_features("Fine Young Cannibals")
```

```{r}
# Frank Sinatra 
full_frank_sinatra <- get_artist_audio_features("Frank Sinatra")
```

```{r}
# Harry Belafonte	
harry_belafonte <- get_artist_audio_features("Harry Belafonte")
```

```{r}
# James Taylor
james_taylor <- get_artist_audio_features("James Taylor")
```

```{r}
# Kanye West	
kanye_west <- get_artist_audio_features("Kanye_West")
```

```{r}
# Mariah Carey	
mariah_carey <- get_artist_audio_features("Mariah Carey")
```

```{r}
# Michael Jackson	
michael_jackson <- get_artist_audio_features("Michael Jackson")
```

```{r}
# Nat King Cole	
nat_king_cole <- get_artist_audio_features("Nat King Cole")
```

```{r}
# Phil Collins
phil_collins <- get_artist_audio_features("Phil Collins")
```

```{r}
# R.E.M. 
r_e_m <- get_artist_audio_features("R.E.M.")
```

```{r}
# Simon & Garfunkel 
simon_garfunkel <- get_artist_audio_features("Simon & Garfunkel")
```

```{r}
# Steve Winwood
steve_winwood <- get_artist_audio_features("Steve Winwood")
```

```{r}
# Stevie Wonder
stevie_wonder <- get_artist_audio_features("Stevie Wonder")
```

```{r}
# Sting
sting <- get_artist_audio_features("sting")
```

```{r}
# Tony Bennett
tony_bennett <- get_artist_audio_features("Tony Bennett")
```

```{r}
# Van Cliburn
van_cliburn <- get_artist_audio_features("Van Cliburn")
```

```{r}
# Garbage
garbage <- get_artist_audio_features("Garbage")
```

```{r}
# Gnarls Barkley
gnarls_barkley <- get_artist_audio_features("Gnarls Barkley")
```

```{r}
# Green Day
green_day <- get_artist_audio_features("Green Day")
```

```{r}
# Gwen Stefani
gwen_stefani <- get_artist_audio_features("Gwen Stefani")
```

```{r}
# Janice Ian
janis_ian <- get_artist_audio_features("Janis Ian")
```

```{r}
# Joan Osborne
joan_osborne <- get_artist_audio_features("Joan Osborne")
```

```{r}
# Lauryn Hill
lauryn_hill <- get_artist_audio_features("Lauryn Hill")
```

```{r}
# Maurice Jarre
maurice_jarre <- get_artist_audio_features("Maurice Jarre")
```

```{r}
# Nilsson
nilsson <- get_artist_audio_features("Nilsson")
```

```{r}
# Paula Cole
paula_cole <- get_artist_audio_features("Paula Cole")
```

```{r}
# Richard Harris
richard_harris <- get_artist_audio_features("Richard Harris")
```

```{r}
# Robert Russell Bennett
robert_russell_bennett <- get_artist_audio_features("Robert Russell Bennett")
```

```{r}
# Rumours - Fleetwood Mac
## Spotify only has three different Rumor albums available: 2017 remastered, deluxe and super deluxe. This album ID is from the super deluxe edition of Rumor.
fleetwood_mac <- spotifyr::get_album_tracks("0BwWUstDMUbgq2NYONRqlu")
fleetwood_mac$Artist <- "Fleetwood Mac"
fleetwood_mac$Album <- "Rumours"

audio <- spotifyr::get_track_audio_features(fleetwood_mac$id)

fleetwood_mac <- left_join(fleetwood_mac, audio, by = "id")

fleetwood_mac_clean <- fleetwood_mac %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# All Things Must Pass - George Harrison
george_harrison_solo <- spotifyr::get_album_tracks("4I4xtHaIFOzhZfp1NIHkY6")
george_harrison_solo$Artist <- "George Harrison"
george_harrison_solo$Album <- "All Things Must Pass"

audio <- spotifyr::get_track_audio_features(george_harrison_solo$id)

george_harrison_solo <- left_join(george_harrison_solo, audio, by = "id")

george_harrison_solo_clean <- george_harrison_solo %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Breezin' - George Benson	
george_benson <- spotifyr::get_album_tracks("1ei5QjnfB7PHINJOH8Gft5")
george_benson$Artist <- "George Benson"
george_benson$Album <- "Breezin'"

audio <- spotifyr::get_track_audio_features(george_benson$id)

george_benson <- left_join(george_benson, audio, by = "id")

george_benson_clean <- george_benson %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Faith - George Michael	
george_michael <- spotifyr::get_album_tracks("34K1Kvskt9arWy8E1Gz3Lw")
george_michael$Artist <- "George Michael"
george_michael$Album <- "Faith"

audio <- spotifyr::get_track_audio_features(george_michael$id)

george_michael <- left_join(george_michael, audio, by = "id")

george_michael_clean <- george_michael %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# What Now My Love - Herb Alpert and the Tijuana Brass	
herb_alpert <- spotifyr::get_album_tracks("5LDqwFbW6XrZtTVnGI8RTN")
herb_alpert$Artist <- "Herb Alpert and the Tijuana Brass"
herb_alpert$Album <- "What Now My Love"

audio <- spotifyr::get_track_audio_features(herb_alpert$id)

herb_alpert <- left_join(herb_alpert, audio, by = "id")

herb_alpert_clean <- herb_alpert %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# River: The Joni Letters - Herbie Hancock	
herbie_hancock <- spotifyr::get_album_tracks("3GwR5VxaMzB01ay6qIT3Yq")
herbie_hancock$Artist <- "Herbie Hancock"
herbie_hancock$Album <- "River: The Joni Letters"

audio <- spotifyr::get_track_audio_features(herbie_hancock$id)

herbie_hancock <- left_join(herbie_hancock, audio, by = "id")

herbie_hancock_clean <- herbie_hancock %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Shaft - Issac Hayes	
issac_hayes <- spotifyr::get_album_tracks("2KIGwFJHrXcyK0VUb5FH9m")
issac_hayes$Artist <- "Isaac Hayes"
issac_hayes$Album <- "Shaft"

audio <- spotifyr::get_track_audio_features(issac_hayes$id)

issac_hayes <- left_join(issac_hayes, audio, by = "id")

issac_hayes_clean <- issac_hayes %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Running on Empty - Jackson Browne	
jackson_browne <- spotifyr::get_album_tracks("24UtAJJRIuHICjdIDqaNhg")
jackson_browne$Artist <- "Jackson Browne"
jackson_browne$Album <- "Running on Empty"

audio <- spotifyr::get_track_audio_features(jackson_browne$id)

jackson_browne <- left_join(jackson_browne, audio, by = "id")

jackson_browne_clean <- jackson_browne %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```
	
```{r}
# Control - Janet Jackson
janet_jackson <- spotifyr::get_album_tracks("7GWkceE5McMVfffd1RGL6Y")
janet_jackson$Artist <- "Janet Jackson"
janet_jackson$Album <- "Control"

audio <- spotifyr::get_track_audio_features(janet_jackson$id)

janet_jackson <- left_join(janet_jackson, audio, by = "id")

janet_jackson_clean <- janet_jackson %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# American Fool - John Cougar
## Name is John Mellencamp on Spotify, went by both names but different in AOTY file
john_cougar <- spotifyr::get_album_tracks("4gouGcdQn9OvjX42xnWrF0")
john_cougar$Artist <- "John Cougar"
john_cougar$Album <- "American Fool"

audio <- spotifyr::get_track_audio_features(john_cougar$id)

john_cougar <- left_join(john_cougar, audio, by = "id")

john_cougar_clean <- john_cougar %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Double Fantasy - John Lennon & Yoko Ono
lennon_ono <- spotifyr::get_album_tracks("1NWA2fPLUAW5df7UGI5thp")
lennon_ono$Artist <- "John Lennon & Yoko Ono"
lennon_ono$Album <- "Double Fantasy"

audio <- spotifyr::get_track_audio_features(lennon_ono$id)

lennon_ono <- left_join(lennon_ono, audio, by = "id")

lennon_ono_clean <- lennon_ono %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Continuum - John Mayer
john_mayer <- spotifyr::get_album_tracks("1Xsprdt1q9rOzTic7b9zYM")
john_mayer$Artist <- "John Mayer"
john_mayer$Album <- "Continuum"

audio <- spotifyr::get_track_audio_features(john_mayer$id)

john_mayer <- left_join(john_mayer, audio, by = "id")

john_mayer_clean <- john_mayer %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# At San Quentin - Johnny Cash
johnny_cash <- spotifyr::get_album_tracks("6bYqwLMVRQzwPQweVzCiry")
johnny_cash$Artist <- "Johnny Cash"
johnny_cash$Album <- "At San Quentin"

audio <- spotifyr::get_track_audio_features(johnny_cash$id)

johnny_cash <- left_join(johnny_cash, audio, by = "id")

johnny_cash_clean <- johnny_cash %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Court and Spark - Joni Mitchell	
joni_mitchell <- spotifyr::get_album_tracks("2akjxkzFolkeV72Yyv5KrM")
joni_mitchell$Artist <- "Joni Mitchell"
joni_mitchell$Album <- "Court and Spark"

audio <- spotifyr::get_track_audio_features(joni_mitchell$id)

joni_mitchell <- left_join(joni_mitchell, audio, by = "id")

joni_mitchell_clean <- joni_mitchell %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Feliciano! - José Feliciano	
jose_feliciano <- spotifyr::get_album_tracks("2uNZs8gPxog0FALe62yeuO")
jose_feliciano$Artist <- "José Feliciano"
jose_feliciano$Album <- "Feliciano!"

audio <- spotifyr::get_track_audio_features(jose_feliciano$id)

jose_feliciano <- left_join(jose_feliciano, audio, by = "id")

jose_feliciano_clean <- jose_feliciano %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Ingenue - k.d. lang		
kd_lang <- spotifyr::get_album_tracks("1XHEQqyatYvfK5cEJfkPeK")
kd_lang$Artist <- "k.d. lang"
kd_lang$Album <- "Ingenue"

audio <- spotifyr::get_track_audio_features(kd_lang$id)

kd_lang <- left_join(kd_lang, audio, by = "id")

kd_lang_clean <- kd_lang %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Tha Carter III - Lil Wayne		
lil_wayne <- spotifyr::get_album_tracks("5BGzOpea6At0Nd7tYtYZOP")
lil_wayne$Artist <- "Lil Wayne"
lil_wayne$Album <- "Tha Carter III"

audio <- spotifyr::get_track_audio_features(lil_wayne$id)

lil_wayne <- left_join(lil_wayne, audio, by = "id")

lil_wayne_clean <- lil_wayne %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Heart Like a Wheel - Linda Ronstadt	
linda_ronstadt <- spotifyr::get_album_tracks("7upKDUGJUjsvfIe6vuVB0b")
linda_ronstadt$Artist <- "Linda Ronstadt"
linda_ronstadt$Album <- "Heart Like a Wheel"

audio <- spotifyr::get_track_audio_features(linda_ronstadt$id)

linda_ronstadt <- left_join(linda_ronstadt, audio, by = "id")

linda_ronstadt_clean <- linda_ronstadt %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Can't Slow Down - Lionel Richie	
lionel_richie <- spotifyr::get_album_tracks("3alZBOvPaK3hgMEEymw4Yr")
lionel_richie$Artist <- "Lionel Richie"
lionel_richie$Album <- "Can't Slow Down"

audio <- spotifyr::get_track_audio_features(lionel_richie$id)

lionel_richie <- left_join(lionel_richie, audio, by = "id")

lionel_richie_clean <- lionel_richie %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```
	
```{r}
# Ray of Light - Madonna	
madonna <- spotifyr::get_album_tracks("6cuNyrSmRjBeekioLdLkvI")
madonna$Artist <- "Madonna"
madonna$Album <- "Ray of Light"

audio <- spotifyr::get_track_audio_features(madonna$id)

madonna <- left_join(madonna, audio, by = "id")

madonna_clean <- madonna %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```
	
```{r}
# Please Hammer Don't Hurt 'Em - MC Hammer
mc_hammer <- spotifyr::get_album_tracks("4r1WecJyt5FOhglysp9zhN")
mc_hammer$Artist <- "MC Hammer"
mc_hammer$Album <- "Please Hammer Don't Hurt 'Em"

audio <- spotifyr::get_track_audio_features(mc_hammer$id)

mc_hammer <- left_join(mc_hammer, audio, by = "id")

mc_hammer_clean <- mc_hammer %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Unforgettable... with Love - Natalie Cole
natalie_cole <- spotifyr::get_album_tracks("3Z4DrrPcAsTWOhDelLNwrK")
natalie_cole$Artist <- "Natalie Cole"
natalie_cole$Album <- "Unforgettable... with Love"

audio <- spotifyr::get_track_audio_features(natalie_cole$id)

natalie_cole <- left_join(natalie_cole, audio, by = "id")

natalie_cole_clean <- natalie_cole %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Year of the Gentleman - Ne-Yo	
neyo <- spotifyr::get_album_tracks("6dTn9vJSxVTIGm4Cu5dH4x")
neyo$Artist <- "Ne-Yo"
neyo$Album <- "Year of the Gentleman"

audio <- spotifyr::get_track_audio_features(neyo$id)

neyo <- left_join(neyo, audio, by = "id")

neyo_clean <- neyo %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Moods - Neil Diamond
neil_diamond <- spotifyr::get_album_tracks("3m4xJJDmVNzsWaJ6OlLTru")
neil_diamond$Artist <- "Neil Diamond"
neil_diamond$Album <- "Moods"

audio <- spotifyr::get_track_audio_features(neil_diamond$id)

neil_diamond <- left_join(neil_diamond, audio, by = "id")

neil_diamond_clean <- neil_diamond %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Vitalogy - Pearl Jam
pearl_jam <- spotifyr::get_album_tracks("5pd9B3KQWKshHw4lnsSLNy")
pearl_jam$Artist <- "Pearl Jam"
pearl_jam$Album <- "Vitalogy"

audio <- spotifyr::get_track_audio_features(pearl_jam$id)

pearl_jam <- left_join(pearl_jam, audio, by = "id")

pearl_jam_clean <- pearl_jam %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```
	
```{r}
# Frampton Comes Alive! - Peter Frampton
peter_frampton <- spotifyr::get_album_tracks("5HmHuAG1kzTqK1N6Ne4zyV")
peter_frampton$Artist <- "Peter Frampton"
peter_frampton$Album <- "Frampton Comes Alive!"

audio <- spotifyr::get_track_audio_features(peter_frampton$id)

peter_frampton <- left_join(peter_frampton, audio, by = "id")

peter_frampton_clean <- peter_frampton %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# So - Peter Gabriel	
peter_gabriel <- spotifyr::get_album_tracks("1vJ8rCzq6BJtKGz9Yf6oT3")
peter_gabriel$Artist <- "Peter Gabriel"
peter_gabriel$Album <- "So"

audio <- spotifyr::get_track_audio_features(peter_gabriel$id)

peter_gabriel <- left_join(peter_gabriel, audio, by = "id")

peter_gabriel_clean <- peter_gabriel %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Stadium Arcadium - Red Hot Chili Peppers
rhcp <- spotifyr::get_album_tracks("7xl50xr9NDkd3i2kBbzsNZ")
rhcp$Artist <- "Red Hot Chili Peppers"
rhcp$Album <- "Stadium Arcadium"

audio <- spotifyr::get_track_audio_features(rhcp$id)

rhcp <- left_join(rhcp, audio, by = "id")

rhcp_clean <- rhcp %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Killing Me Softly - Roberta Flack
roberta_flack <- spotifyr::get_album_tracks("4GxrvKiysSiDU1HHifh1PA")
roberta_flack$Artist <- "Roberta Flack"
roberta_flack$Album <- "Killing Me Softly"

audio <- spotifyr::get_track_audio_features(roberta_flack$id)

roberta_flack <- left_join(roberta_flack, audio, by = "id")

roberta_flack_clean <- roberta_flack %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Seal - Seal
seal <- spotifyr::get_album_tracks("1mSECpFqHRW6leG4idqTE1")
seal$Artist <- "Seal"
seal$Album <- "Seal"

audio <- spotifyr::get_track_audio_features(seal$id)

seal <- left_join(seal, audio, by = "id")

seal_clean <- seal %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Come on Over - Shania Twain	
shania_twain <- spotifyr::get_album_tracks("4UMe0Ods7kygK6OISasZe9")
shania_twain$Artist <- "Shania Twain"
shania_twain$Album <- "Come on Over"

audio <- spotifyr::get_track_audio_features(shania_twain$id)

shania_twain <- left_join(shania_twain, audio, by = "id")

shania_twain_clean <- shania_twain %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# The Globe Sessions - Sheryl Crow	
sheryl_crow <- spotifyr::get_album_tracks("08enrSAkHTYkQwhRlKXQgB")
sheryl_crow$Artist <- "Sheryl Crow"
sheryl_crow$Album <- "The Globe Sessions"

audio <- spotifyr::get_track_audio_features(sheryl_crow$id)

sheryl_crow <- left_join(sheryl_crow, audio, by = "id")

sheryl_crow_clean <- sheryl_crow %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Brahms: Concerto No. 2 in B-Flat - Sviatoslav Richter
s_richter <- spotifyr::get_album_tracks("7lujnnMMa40f9xfQsUWB8D")
s_richter$Artist <- "Sviatoslav Richter"
s_richter$Album <- "Brahms: Concerto No. 2 in B-Flat"

audio <- spotifyr::get_track_audio_features(s_richter$id)

s_richter <- left_join(s_richter, audio, by = "id")

s_richter_clean <- s_richter %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```
	
```{r}
# The Age of Aquarius - The 5th Dimension
the_dimension <- spotifyr::get_album_tracks("1kVipwgtVNAaHM7Py341Ch")
the_dimension$Artist <- "The 5th Dimension"
the_dimension$Album <- "The Age of Aquarius"

audio <- spotifyr::get_track_audio_features(the_dimension$id)

the_dimension <- left_join(the_dimension, audio, by = "id")

the_dimension_clean <- the_dimension %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# The Score - The Fugees
the_fugees <- spotifyr::get_album_tracks("18XFe4CPBgVezXkxZP6rTb")
the_fugees$Artist <- "The Fugees"
the_fugees$Album <- "The Score"

audio <- spotifyr::get_track_audio_features(the_fugees$id)

the_fugees <- left_join(the_fugees, audio, by = "id")

the_fugees_clean <- the_fugees %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Some Girls - The Rolling Stones
the_rolling_stone <- spotifyr::get_album_tracks("1Jv2AqzhgsduUik2p4k3cS")
the_rolling_stone$Artist <- "The Rolling Stones"
the_rolling_stone$Album <- "Some Girls"

audio <- spotifyr::get_track_audio_features(the_rolling_stone$id)

the_rolling_stone <- left_join(the_rolling_stone, audio, by = "id")

the_rolling_stone_clean <- the_rolling_stone %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Mellon Collie and the Infinite Sadness - The Smashing Pumpkins	
smashing_pumpkins <- spotifyr::get_album_tracks("55RhFRyQFihIyGf61MgcfV")
smashing_pumpkins$Artist <- "The Smashing Pumpkins"
smashing_pumpkins$Album <- "Mellon Collie and the Infinite Sadness"

audio <- spotifyr::get_track_audio_features(smashing_pumpkins$id)

smashing_pumpkins <- left_join(smashing_pumpkins, audio, by = "id")

smashing_pumpkins_clean <- smashing_pumpkins %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Full Moon Fever- Tom Petty	
tom_petty <- spotifyr::get_album_tracks("5d71Imt5CIb7LpQwDMQ093")
tom_petty$Artist <- "Tom Petty"
tom_petty$Album <- "Full Moon Fever"

audio <- spotifyr::get_track_audio_features(tom_pettys$id)

tom_petty <- left_join(tom_petty, audio, by = "id")

tom_petty_clean <- tom_petty %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Toto IV - Toto	
toto <- spotifyr::get_album_tracks("62U7xIHcID94o20Of5ea4D")
toto$Artist <- "Toto"
toto$Album <- "Toto IV"

audio <- spotifyr::get_track_audio_features(toto$id)

toto <- left_join(toto, audio, by = "id")

toto_clean <- toto %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# The Bodyguard - Whitney Houston
whitney <- spotifyr::get_album_tracks("7JVJlkNNobS0GSoy4tCS96")
whitney$Artist <- "Whitney Houston"
whitney$Album <- "The Bodyguard"

audio <- spotifyr::get_track_audio_features(whitney$id)
whitney <- left_join(whitney, audio, by = "id")

whitney_clean <- whitney %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Tracy Chapman	 - Tracy Chapman	
tracy_chapman <- spotifyr::get_album_tracks("6hmmX5UP4rIvOpGSaPerV8")
tracy_chapman$Artist <- "Tracy Chapman"
tracy_chapman$Album <- "Tracy Chapman"

audio <- spotifyr::get_track_audio_features(tracy_chapman$id)
tracy_chapman <- left_join(tracy_chapman, audio, by = "id")

tracy_chapman_clean <- tracy_chapman %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Confessions - Usher
usher <- spotifyr::get_album_tracks("1RM6MGv6bcl6NrAG8PGoZk")
usher$Artist <- "Usher"
usher$Album <- "Confessions"

audio <- spotifyr::get_track_audio_features(usher$id)
usher <- left_join(usher, audio, by = "id")

usher_clean <- usher %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# It Must Be Him - Vikki Carr
vikki_carr <- spotifyr::get_album_tracks("77ECOoesygcTfXRhn4rteH")
vikki_carr$Artist <- "Vikki Carr"
vikki_carr$Album <- "It Must Be Him"

audio <- spotifyr::get_track_audio_features(vikki_carr$id)
vikki_carr <- left_join(vikki_carr, audio, by = "id")

vikki_carr_clean <- vikki_carr %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Wilson Phillips	 - Wilson Phillips
wilson_phillips <- spotifyr::get_album_tracks("1Xi55xFMaymXdSWshmxhw2")
wilson_phillips$Artist <- "Wilson Phillips"
wilson_phillips$Album <- "Wilson Phillips"

audio <- spotifyr::get_track_audio_features(wilson_phillips$id)
wilson_phillips <- left_join(wilson_phillips, audio, by = "id")

wilson_phillips_clean <- wilson_phillips %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Various Artists - Black Panther: The Album, Music from and Inspired By - 2019
black_panther <- spotifyr::get_album_tracks("3pLdWdkj83EYfDN6H2N8MR")
black_panther$Artist <- "Various Artists"
black_panther$Album <- "Black Panther: The Album, Music from and Inspired By"

audio <- spotifyr::get_track_audio_features(black_panther$id)
black_panther <- left_join(black_panther, audio, by = "id")

black_panther_clean <- black_panther %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Various Artists - O Brother, Where Art Thou? Soundtrack - 2002
o_brother <- spotifyr::get_album_tracks("7gzX88qS3Vx2r87g5pbdfJ")
o_brother$Artist <- "Various Artists"
o_brother$Album <- "O Brother, Where Art Thou? Soundtrack"

audio <- spotifyr::get_track_audio_features(o_brother$id)
o_brother <- left_join(o_brother, audio, by = "id")

o_brother_clean <- o_brother %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Various Artists - Beauty and the Beast - 1993
beauty_beast <- spotifyr::get_album_tracks("3O5p9VNddbwvqWTdYKEqV5")

beauty_beast$Artist <- "Various Artists"
beauty_beast$Album <- "Beauty and the Beast"

audio <- spotifyr::get_track_audio_features(beauty_beast$id)
beauty_beast <- left_join(beauty_beast, audio, by = "id")

beauty_beast_clean <- beauty_beast %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Various Artists - Waiting to Exhale: Original Soundtrack Album - 1997
waiting_exhale <- spotifyr::get_album_tracks("2EHFZkzTbRFDt1tomCBToM")

waiting_exhale$Artist <- "Various Artists"
waiting_exhale$Album <- "Waiting to Exhale: Original Soundtrack Album"

audio <- spotifyr::get_track_audio_features(waiting_exhale$id)
waiting_exhale <- left_join(waiting_exhale, audio, by = "id")

waiting_exhale_clean <- waiting_exhale %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```
	
```{r}
# Various Artists - West Side Story Soundtrack - 1962
west_side <- spotifyr::get_album_tracks("1kA4RO70idrEQkOX3zlRfa")

west_side$Artist <- "Various Artists"
west_side$Album <- "West Side Story Soundtrack"

audio <- spotifyr::get_track_audio_features(west_side$id)
west_side <- left_join(west_side, audio, by = "id")

west_side_clean <- west_side %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```
	 
```{r}
# Various Artists - Funny Girl (Original Broadway Cast Recording) - 1965
funny_girl <- spotifyr::get_album_tracks("0G8qWYPobQUV9wDm2XABPp")

funny_girl$Artist <- "Various Artists"
funny_girl$Album <- "Funny Girl (Original Broadway Cast Recording)"

audio <- spotifyr::get_track_audio_features(funny_girl$id)
funny_girl <- left_join(funny_girl, audio, by = "id")

funny_girl_clean <- funny_girl %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Various Artists - The Sound of Music Soundtrack - 1996
sound_music <- spotifyr::get_album_tracks("583SgyGBxtEzsk9J8zBqiy")

sound_music$Artist <- "Various Artists"
sound_music$Album <- "The Sound of Music Soundtrack"

audio <- spotifyr::get_track_audio_features(sound_music$id)
sound_music <- left_join(sound_music, audio, by = "id")

sound_music_clean <- sound_music %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Various Artists - Grease Original Soundtrack Album - 1979
grease <- spotifyr::get_album_tracks("5n47Dui0H3pGpZSOxITmoq")

grease$Artist <- "Various Artists"
grease$Album <- "Grease Original Soundtrack Album"

audio <- spotifyr::get_track_audio_features(grease$id)
grease <- left_join(grease, audio, by = "id")

grease_clean <- grease %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Various Artists - Flashdance Soundtrack - 1984
flashdance <- spotifyr::get_album_tracks("3R6Z3Hp8EMdhgkA5t89NiL")

flashdance$Artist <- "Various Artists"
flashdance$Album <- "Flashdance Soundtrack"

audio <- spotifyr::get_track_audio_features(flashdance$id)
flashdance <- left_join(flashdance, audio, by = "id")

flashdance_clean <- flashdance %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Various Artists - Saturday Night Fever Soundtrack - 1979
saturday_night <- spotifyr::get_album_tracks("3xaCKtqadm4KnviPFKEjs7")

saturday_night$Artist <- "Various Artists"
saturday_night$Album <- "Saturday Night Fever Soundtrack"

audio <- spotifyr::get_track_audio_features(saturday_night$id)
saturday_night <- left_join(saturday_night, audio, by = "id")

saturday_night_clean <- saturday_night %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Private Dancer - Tina Turner
tina_turner <- spotifyr::get_album_tracks("7gVHUNPQr0AE2A0Yf5MjqR")
tina_turner$Artist <- "Tina Turner"
tina_turner$Album <- "Private Dancer"

audio <- spotifyr::get_track_audio_features(tina_turner$id)

tina_turner <- left_join(tina_turner, audio, by = "id")

tina_turner_clean <- tina_turner %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Supernatural - Santana
santana <- spotifyr::get_album_tracks("10aiDpdFGyfCFEcqpx6XTq")
santana$Artist <- "Santana"
santana$Album <- "Supernatural"

audio <- spotifyr::get_track_audio_features(santana$id)

santana <- left_join(santana, audio, by = "id")

santana_clean <- santana %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# september of my years - Frank Sinatra
franksin_2 <- spotifyr::get_album_tracks("3DdN3GRJj8YS0V0fiyXtbt")
franksin_2$Artist <- "Frank Sinatra"
franksin_2$Album <- "september of my years"

audio <- spotifyr::get_track_audio_features(franksin_2$id)

franksin_2 <- left_join(franksin_2, audio, by = "id")

franksin_2_clean <- franksin_2 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Trilogy: Past Present Future - Frank Sinatra
franksin_1 <- spotifyr::get_album_tracks("4Cv61B08yHx3fwkylkhCxe")
franksin_1$Artist <- "Frank Sinatra"
franksin_1$Album <- "Trilogy: Past Present Future"

audio <- spotifyr::get_track_audio_features(franksin_1$id)

franksin_1 <- left_join(franksin_1, audio, by = "id")

franksin_1_clean <- franksin_1 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# nice 'n' easy - Frank Sinatra
franksin_3 <- spotifyr::get_album_tracks("2Xp6c8OMMolIoix6KLyun2")
franksin_3$Artist <- "Frank Sinatra"
franksin_3$Album <- "nice 'n' easy"

audio <- spotifyr::get_track_audio_features(franksin_3$id)

franksin_3 <- left_join(franksin_3, audio, by = "id")

franksin_3_clean <- franksin_3 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```
	
```{r}
# frank sinatra sings for only the lonely - Frank Sinatra
franksin_4 <- spotifyr::get_album_tracks("0xV0zM1RVaVQ8LaUp6bLWR")
franksin_4$Artist <- "Frank Sinatra"
franksin_4$Album <- "frank sinatra sings for only the lonely"

audio <- spotifyr::get_track_audio_features(franksin_4$id)

franksin_4 <- left_join(franksin_4, audio, by = "id")

franksin_4_clean <- franksin_4 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# come fly with me - Frank Sinatra
franksin_5 <- spotifyr::get_album_tracks("66v9QmjAj0Wwhh2OpbU4BE")
franksin_5$Artist <- "Frank Sinatra"
franksin_5$Album <- "come fly with me"

audio <- spotifyr::get_track_audio_features(franksin_4$id)

franksin_5 <- left_join(franksin_5, audio, by = "id")

franksin_5_clean <- franksin_5 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# come dance with me! - Frank Sinatra
franksin_6 <- spotifyr::get_album_tracks("2XgFfM6SNKtNLGcN3joZro")
franksin_6$Artist <- "Frank Sinatra"
franksin_6$Album <- "come dance with me!"

audio <- spotifyr::get_track_audio_features(franksin_6$id)

franksin_6 <- left_join(franksin_6, audio, by = "id")

franksin_6_clean <- franksin_6 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# déjà vu - Crosby, Stills, Nash and Young
crosby_young <- spotifyr::get_album_tracks("5bHkK1X4WEOzNvRhehvOcb")
crosby_young$Artist <- "Crosby, Stills, Nash and Young"
crosby_young$Album <- "déjà vu"

audio <- spotifyr::get_track_audio_features(crosby_young$id)

crosby_young <- left_join(crosby_young, audio, by = "id")

crosby_young_clean <- crosby_young %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# i.i - Bon Iver
bon_iver <- spotifyr::get_album_tracks("54DU59anGQsdrFP7utpshG")
bon_iver$Artist <- "Bon Iver"
bon_iver$Album <- "i, i"

audio <- spotifyr::get_track_audio_features(bon_iver$id)

bon_iver <- left_join(bon_iver, audio, by = "id")

bon_iver_clean <- bon_iver %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# i.i - Bon Iver
bon_iver <- spotifyr::get_album_tracks("54DU59anGQsdrFP7utpshG")
bon_iver$Artist <- "Bon Iver"
bon_iver$Album <- "cuz i love you (deluxe)"

audio <- spotifyr::get_track_audio_features(bon_iver$id)

bon_iver <- left_join(bon_iver, audio, by = "id")

bon_iver_clean <- bon_iver %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# morning phase - Beck
beck <- spotifyr::get_album_tracks("2Qx7dgA5VjX8JDQaXVxzHu")
beck$Artist <- "Beck"
beck$Album <- "morning phase"

audio <- spotifyr::get_track_audio_features(beck$id)

beck <- left_join(beck, audio, by = "id")

beck_clean <- beck %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# midnite vultures	- Beck 
beck_2 <- spotifyr::get_album_tracks("5Mk8LGoWoPg0igqQXprzfR")
beck_2$Artist <- "Beck"
beck_2$Album <- "midnite vultures"

audio <- spotifyr::get_track_audio_features(beck_2$id)

beck_2 <- left_join(beck_2, audio, by = "id")

beck_2_clean <- beck_2 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# beyoncé - Beyoncé  
beyonce <- spotifyr::get_album_tracks("2UJwKSBUz6rtW4QLK74kQu")
beyonce$Artist <- "Beyoncé "
beyonce$Album <- "beyoncé"

audio <- spotifyr::get_track_audio_features(beyonce$id)

beyonce <- left_join(beyonce, audio, by = "id")

beyonce_clean <- beyonce %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# x - Ed Sheeran 
ed_sheeran <- spotifyr::get_album_tracks("1xn54DMo2qIqBuMqHtUsFd")
ed_sheeran$Artist <- "Ed Sheeran "
ed_sheeran$Album <- "x"

audio <- spotifyr::get_track_audio_features(ed_sheeran$id)

ed_sheeran <- left_join(ed_sheeran, audio, by = "id")

ed_sheeran_clean <- ed_sheeran %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# purpose - Justin Bieber 
justin_b <- spotifyr::get_album_tracks("6Fr2rQkZ383FcMqFyT7yPr")
justin_b$Artist <- "Justin Bieber"
justin_b$Album <- "purpose"

audio <- spotifyr::get_track_audio_features(justin_b$id)

justin_b <- left_join(justin_b, audio, by = "id")

justin_b_clean <- justin_b %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# traveling wilburys vol. 1 -	Traveling Wilburys 
travel <- spotifyr::get_album_tracks("7K3OJcdtRxv7miXfQBzvbi")
travel$Artist <- "Traveling Wilburys"
travel$Album <- "traveling wilburys vol. 1"

audio <- spotifyr::get_track_audio_features(travel$id)

travel <- left_join(travel, audio, by = "id")

travel_clean <- travel %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# ...but seriously	- Phil Collins 
phil <- spotifyr::get_album_tracks("2sS9l8uc3d3UsK9unJyrD8")
phil$Artist <- "Phil Collins"
phil$Album <- "...but seriously"

audio <- spotifyr::get_track_audio_features(phil$id)

phil <- left_join(phil, audio, by = "id")

phil_clean <- phil %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# odelay - Beck 
beck3 <- spotifyr::get_album_tracks("3VCaLNEZTCVRwB8fIpmuM7")
beck3$Artist <- "Beck "
beck3$Album <- "odelay"

audio <- spotifyr::get_track_audio_features(beck3$id)

beck3 <- left_join(beck3, audio, by = "id")

beck3_clean <- beck3 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# sgt. pepper's lonely hearts club band - The Beatles 
sgt <- spotifyr::get_album_tracks("6QaVfG1pHYl1z15ZxkvVDW")
sgt$Artist <- "The Beatles"
sgt$Album <- "sgt. pepper's lonely hearts club band"

audio <- spotifyr::get_track_audio_features(sgt$id)

sgt <- left_join(sgt, audio, by = "id")

sgt_clean <- sgt %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# by the time i get to phoenix	- Glen Campbell	
gc <- spotifyr::get_album_tracks("29tTA46kurlOioRkjBqOMS")
gc$Artist <- "Glen Campbell"
gc$Album <- "by the time i get to phoenix"

audio <- spotifyr::get_track_audio_features(gc$id)

gc <- left_join(gc, audio, by = "id")

gc_clean <- gc %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# no jacket required -	Phil Collins	
pc <- spotifyr::get_album_tracks("1rVhockt4RAiZFaK3M3zPB")
pc$Artist <- "Phil Collins	"
pc$Album <- "no jacket required"

audio <- spotifyr::get_track_audio_features(pc$id)

pc <- left_join(pc, audio, by = "id")

pc_clean <- pc %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# graceland	 - Paul Simon 
ps <- spotifyr::get_album_tracks("6WgGWYw6XXQyLTsWt7tXky")
ps$Artist <- "Paul Simon"
ps$Album <- "graceland"

audio <- spotifyr::get_track_audio_features(ps$id)

ps <- left_join(ps, audio, by = "id")

ps_clean <- ps %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# help! - The Beatles 
beatles <- spotifyr::get_album_tracks("0PT5m6hwPRrpBwIHVnvbFX")
beatles$Artist <- "The Beatles"
beatles$Album <- "help!"

audio <- spotifyr::get_track_audio_features(beatles$id)

beatles <- left_join(beatles, audio, by = "id")

beatles_clean <- beatles %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# revolver	 - The Beatles 
beatles1 <- spotifyr::get_album_tracks("3PRoXYsngSwjEQWR5PsHWR")
beatles1$Artist <- "The Beatles"
beatles1$Album <- "revolver"

audio <- spotifyr::get_track_audio_features(beatles1$id)

beatles1 <- left_join(beatles1, audio, by = "id")

beatles1_clean <- beatles1 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# abbey road	The Beatles 
beatles2 <- spotifyr::get_album_tracks("0ETFjACtuP2ADo6LFhL6HN")
beatles2$Artist <- "The Beatles"
beatles2$Album <- "abbey road"

audio <- spotifyr::get_track_audio_features(beatles2$id)

beatles2 <- left_join(beatles2, audio, by = "id")

beatles2_clean <- beatles2 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# magical mystery tour	The Beatles 
beatles3 <- spotifyr::get_album_tracks("2BtE7qm1qzM80p9vLSiXkj")
beatles3$Artist <- "The Beatles"
beatles3$Album <- "magical mystery tour"

audio <- spotifyr::get_track_audio_features(beatles3$id)

beatles3 <- left_join(beatles3, audio, by = "id")

beatles3_clean <- beatles3 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# sweet baby james - James Taylor 
james_t <- spotifyr::get_album_tracks("1HiG0ukRmFPN13EVcf98Jx")
james_t$Artist <- "James Taylor"
james_t$Album <- "sweet baby james"

audio <- spotifyr::get_track_audio_features(james_t$id)

james_t <- left_join(james_t, audio, by = "id")

james_t_clean <- james_t %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# between the lines	 Janis Ian 
janis <- spotifyr::get_album_tracks("6RjDm4cjV3MFndKrpLUxpO")
janis$Artist <- "Janis Ian "
janis$Album <- "between the lines"

audio <- spotifyr::get_track_audio_features(janis$id)

janis <- left_join(janis, audio, by = "id")

janis_clean <- janis %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# one of these nights	- eagles 
eagles <- spotifyr::get_album_tracks("0F77QekrNe8vVAjU2sepja")
eagles$Artist <- "Eagles"
eagles$Album <- "one of these nights"

audio <- spotifyr::get_track_audio_features(eagles$id)

eagles <- left_join(eagles, audio, by = "id")

eagles_clean <- eagles %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# hotel california -	eagles 
eagles2 <- spotifyr::get_album_tracks("2widuo17g5CEC66IbzveRu")
eagles2$Artist <- "Eagles"
eagles2$Album <- "hotel california"

audio <- spotifyr::get_track_audio_features(eagles2$id)

eagles2 <- left_join(eagles2, audio, by = "id")

eagles2_clean <- eagles2 %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# let's dance david bowie 
david_bowie <- spotifyr::get_album_tracks("4NwG11AsDJluT732lSjMrV")
david_bowie$Artist <- "David Bowie"
david_bowie$Album <- "let's dance"

audio <- spotifyr::get_track_audio_features(david_bowie$id)

david_bowie <- left_join(david_bowie, audio, by = "id")

david_bowie_clean <- david_bowie %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# synchronicity the police 
police <- spotifyr::get_album_tracks("5W9OT0a5iZlBr83a9WMKFY")
police$Artist <- "The Police"
police$Album <- "synchronicity"

audio <- spotifyr::get_track_audio_features(police$id)

police <- left_join(police, audio, by = "id")

police_clean <- police %>% select(-c(artists:disc_number, href:is_local, preview_url:external_urls.spotify, type.y:time_signature))
```

```{r}
# Bind all of the data together for cases where I just used `get_artist_audio_features`
raw_df_3 <- rbind(robert_russell_bennett, richard_harris, paula_cole, nilsson, maurice_jarre, lauryn_hill, joan_osborne, janis_ian, gwen_stefani, green_day, gnarls_barkley, garbage, fine_young_cannibals, elton_john, eric_clapton, full_frank_sinatra, harry_belafonte, james_taylor, kanye_west, mariah_carey, michael_jackson, nat_king_cole, phil_collins, r_e_m, simon_garfunkel, steve_winwood, stevie_wonder, sting, tony_bennett, van_cliburn, whitney_houston, erich_leinsdorf, eddy_arnold, ed_ames, eagles, donald_fagen, don_mclean, don_henley, dire_straits, crosby_stills_nash, crosby_stills_nash_young, coldplay, christopher_cross, charlie_rich, celine_dion, carpenters, boz_scaggs, bonnie_raitt, bobby_mcferrin, bobbie_gentry, bob_newhart, blood_sweat_tears, billy_joel, bette_middler, barry_manilow, babyface, andy_williams, amy_winehouse, amy_grant, allan_sherman, alicia_keys, alanis_morissette, al_hirt, chicago)

clean_df_3 <- cbind(Artist = raw_df_3$artist_name,
                 Album = raw_df_3$album_name,
                 Song = raw_df_3$track_name,
                 Danceability = raw_df_3$danceability,
                 Energy = raw_df_3$energy,
                 Loudness = raw_df_3$loudness,
                 Speechiness = raw_df_3$speechiness,
                 Acousticness = raw_df_3$acousticness,
                 Instrumentalness = raw_df_3$instrumentalness,
                 Liveness = raw_df_3$liveness,
                 Valence = raw_df_3$valence,
                 Tempo = raw_df_3$tempo,
                 Duration = raw_df_3$duration_ms,
                 Explicit = raw_df_3$explicit)

clean_df_3 <- as.data.frame(clean_df_3)
```

```{r}
raw_df_4 <- rbind(fleetwood_mac_clean, george_harrison_solo_clean, george_benson_clean, george_michael_clean, herb_alpert_clean, herbie_hancock_clean, issac_hayes_clean, jackson_browne_clean, janet_jackson_clean, john_cougar_clean, lennon_ono_clean, john_mayer_clean, johnny_cash_clean, joni_mitchell_clean, jose_feliciano_clean, kd_lang_clean, lil_wayne_clean, linda_ronstadt_clean, lionel_richie_clean, madonna_clean, mc_hammer_clean, natalie_cole_clean, neyo_clean, neil_diamond_clean, pearl_jam_clean, peter_frampton_clean, peter_gabriel_clean, rhcp_clean, roberta_flack_clean, seal_clean, shania_twain_clean, sheryl_crow_clean, s_richter_clean, the_dimension_clean, the_fugees_clean, the_rolling_stone_clean, smashing_pumpkins_clean, tom_petty_clean, toto_clean, tracy_chapman_clean, usher_clean, vikki_carr_clean, wilson_phillips_clean, black_panther_clean, o_brother_clean, beauty_beast_clean,  waiting_exhale_clean, west_side_clean, funny_girl_clean, sound_music_clean, grease_clean, flashdance_clean, saturday_night_clean, whitney_clean, tina_turner_clean, santana_clean, franksin_1_clean, franksin_2_clean, franksin_3_clean, franksin_4_clean, franksin_5_clean, franksin_6_clean, crosby_young_clean,bon_iver_clean, beck_clean, beck_2_clean, beyonce_clean, ed_sheeran_clean, justin_b_clean, travel_clean, phil_clean, beck3_clean, sgt_clean, gc_clean, pc_clean, ps_clean, beatles_clean, beatles1_clean, beatles2_clean, beatles3_clean, james_t_clean, janis_clean, eagles_clean, eagles2_clean, david_bowie_clean, police_clean)

clean_df_4 <- cbind(Artist = raw_df_4$Artist,
                 Album = raw_df_4$Album,
                 Song = raw_df_4$name,
                 Danceability = raw_df_4$danceability,
                 Energy = raw_df_4$energy,
                 Loudness = raw_df_4$loudness,
                 Speechiness = raw_df_4$speechiness,
                 Acousticness = raw_df_4$acousticness,
                 Instrumentalness = raw_df_4$instrumentalness,
                 Liveness = raw_df_4$liveness,
                 Valence = raw_df_4$valence,
                 Tempo = raw_df_4$tempo,
                 Duration = raw_df_4$duration_ms.x,
                 Explicit = raw_df_4$explicit)

clean_df_4 <- as.data.frame(clean_df_4)
```

```{r}
# Join everything together
albums <- rbind(albums, clean_df_1, clean_df_2, clean_df_3, clean_df_4)
```

```{r}
# Removing artists that got pulled from Spotify that aren't in AOTY: Becky G, John Mellencamp (This artisti also goes by John Cougar and his album under John Cougar is in AOTY but not John Mellencamp), مختلف الفنانين
albums <- albums[!(albums$Artist=="John Mellencamp" | albums$Artist=="مختلف الفنانين" | albums$Artist=="Becky G"),]
```

```{r}
# Making all of the album names to lower case to prepare for left join of albums and AOTY dataframes
albums$Album <- tolower(albums$Album)
AOTY$Album <- tolower(AOTY$Album)
```

```{r}
#Changing album spotify pull album titles that don't correspond to AOTY resulting in NA during left_join
albums$Album[469:486] <- "cuz i love you (deluxe)"
albums$Album[1562:1574] <- "big whiskey & the groogrux king"
albums$Album[28356:34266] <- "the e.n.d."
albums$Album[2590:2626] <- "i am... sasha fierce"
albums$Album[5497:5507] <- "girl"
albums$Album[42833:42872] <- "love. angel. music. baby."
albums$Album[48322:48380] <- "history: past, present and future, book i"
albums$Album[14817:14827] <- "the barbra streisand album"
albums$Album[36038:36047] <- "getz/gilberto"
albums$Album[62906:62925] <- "blood, sweat & tears"
albums$Album[28027:28057] <- "ella fitzgerald sings the irving berlin songbook"
albums$Album[53191:53193] <- "tchaikovsky: concerto no. 1 in b flat minor, op. 23"
albums$Album[46879:46897] <- "belafonte at carnegie hall"
albums$Album[16807:16820] <- "more music from peter gunn"
albums$Album[53211:53216] <- "rachmaninoff piano concerto no. 3"
albums$Album[40632:40640] <- "victory at sea, vol. 1"
albums$Album[18749:18760] <- "breakfast at tiffany's soundtrack"
albums$Album[24918:24941] <- "modern sounds in country and western music"
albums$Album[65736:65747] <- "days of wine and roses and other tv requests"
albums$Album[18691:18702] <- "the pink panther"
albums$Album[42037:42081] <- "doctor zhivago soundtrack"
albums$Album[69890:69914] <- "chicago"
albums$Album[30908:30925] <- "band on the run"
albums$Album[33816:40175] <- "star wars soundtrack"
albums$Album[48395:48418] <- "bad"
albums$Album[23820:23835] <- "sign o' the times"
```

```{r}
# Combining AOTY and albums dataframe to one dataframe
AOTY_Spotify <- left_join(AOTY, albums, by = c("Album"))
```

```{r}
write_csv(AOTY_Spotify, "AOTY_Spotify.csv")
saveRDS(AOTY_Spotify, "AOTY_Spotify.RDS")
```
----------

```{r}
#Loading AOTY_Spotify dataframe so I don't have to run the entire code
setwd("/Users/bolee/Desktop/QMSS/Spring20/DataViz/Group_R_Spotify")
AOTY_Spotify <- read.csv("AOTY_Spotify/AOTY_Spotify.csv")
```

```{r}
# Creating dataframe with average audio features we will be using for visualization
AOTY_Avg <- AOTY_Spotify  %>% 
  group_by(Album) %>% 
  summarise(Artist = first(Artist), Year = first(Year), Win = first(Win), Avg_Energy = mean(Energy, na.rm = TRUE), Avg_Danceability = mean(Danceability, na.rm =TRUE), Avg_Loudness = mean(Loudness, na.rm = TRUE), Avg_Valence = mean(Valence, na.rm = TRUE), Avg_Tempo = mean(Tempo, na.rm = TRUE)) 
#Add in popularity score
```

```{r}
write_csv(AOTY_Avg, "AOTY_Avg.csv")
saveRDS(AOTY_Avg, "AOTY_Avg.RDS")
```


